Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Proof-of-Concept V}}

### 2014-07-21 Paper.tex
Explicit definition of RLP in transaction trie.

\begin{description}
\item[nonce] A scalar value equal to the number of transactions sent by the sender; formally $T_n$.
\item[value] A scalar value equal to the number of Wei to be transferred to the message call's recipient or, in the case of contract creation, as an endowment to the newly created account; formally $T_v$.
\item[gasPrice] A scalar value equal to the number of Wei to be paid per unit of \textit{gas} for all computation costs incurred as a result of the execution of this transaction; formally $T_p$.
\item[gasLimit] A scalar value equal to the maximum amount of gas that should be used in executing this transaction. This is paid up-front, before any computation is done and may not be increased later; formally $T_g$.
\item[to] The 160-bit address of the message call's recipient or the zero address for a contract creation transaction; formally $T_t$.
\item[v, r, s] Values corresponding to the signature of the transaction and used to determine the sender of the transaction; formally $T_w$, $T_r$ and $T_s$. This is expanded in Appendix \ref{app:signing}.
\end{description}

@@

We can assert its validity if and only if it satisfies several conditions: It must be internally consistent with the uncle and transaction block hashes and the given transactions $B_\mathbf{T}$, when executed in order on the base state $\boldsymbol{\sigma}$ (derived from the final state of the parent block), result in a new state of the identity $H_r$:
\begin{equation}
\begin{array}[t]{lclc}
H_u &\equiv& \mathtt{\small SHA3}(\mathtt{\small RLP}(L_H^*(B_\mathbf{U}))) & \wedge \\
H_t &\equiv& \mathtt{\small TRIE}(\{\forall i < \lVert B_\mathbf{T} \rVert: (i, B_\mathbf{R}[i])\}) & \wedge \\
H_r &\equiv& \mathtt{\small TRIE}(L_S(\Pi(\boldsymbol{\sigma}, B))) &
\end{array}
\end{equation}

@@

The component types are defined thus:
\begin{equation}
\begin{array}[t]{lclclcl}
H_p \in \mathbb{B}_{32} & \wedge & H_u \in \mathbb{B}_{32} & \wedge & H_b \in \mathbb{B}_{20} & \wedge \\
H_r \in \mathbb{B}_{32} & \wedge & H_t \in \mathbb{B}_{32} & \wedge & H_d \in \mathbb{P} & \wedge \\
H_s \in \mathbb{P} & \wedge & H_x \in \mathbb{B} & \wedge & H_b \in \mathbb{B}_{32} &&
\end{array}
\end{equation}

@@

The canonical gas limit of a block of header $H$ is defined as $L(H)$:
\begin{eqnarray}
L(H) & \equiv & \begin{cases}
10^6 & \text{if} \quad H_i = 0\\
10^4 & \text{if} \quad L'(H) < 10^4\\
L'(H) & \text{otherwise}
\end{cases}\\
L'(H) & \equiv & \big\lfloor \frac{1023 {P(H)_H}_l + \lfloor \frac{6}{5}{P(H)_H}_u \rfloor}{1024}\big\rfloor
\end{eqnarray}

$H_s$ is the timestamp of block $H$ and must fulfill the relation:
\begin{equation}
H_s > {P(H)_H}_s
\end{equation}

@@

This is the foundation of the security of the blockchain and is the fundamental reason why a malicious node cannot propagate newly created blocks that would otherwise overwrite (``rewrite'') history. Because the nonce must satisfy this requirement, and because satisfaction of this requirement depends on the contents of the block and in turn its composed transactions, creating new, valid, blocks is difficult and, over time, requires approximately the total compute power of the trustworthy portion of the mining peers.

@@

The given \textbf{gasUsed} and \textbf{minGasLimit} must correspond faithfully to the transactions listed. In the case of ${B_H}_m$, the minimum gas limit, all transactions included in the transaction receipt must have a gas price, ${T_0}_p$, that is at least this value:
\begin{equation}
\forall \; T \in B_\mathbf{T}: T_p \geq {B_H}_m
\end{equation}

@@

>>>>

\begin{description}
\item[nonce] A scalar value equal to the number of transactions sent by the sender; formally $T_n$.
\item[gasPrice] A scalar value equal to the number of Wei to be paid per unit of \textit{gas} for all computation costs incurred as a result of the execution of this transaction; formally $T_p$.
\item[gasLimit] A scalar value equal to the maximum amount of gas that should be used in executing this transaction. This is paid up-front, before any computation is done and may not be increased later; formally $T_g$.
\item[to] The 160-bit address of the message call's recipient or the zero address for a contract creation transaction; formally $T_t$.
\item[value] A scalar value equal to the number of Wei to be transferred to the message call's recipient or, in the case of contract creation, as an endowment to the newly created account; formally $T_v$.
\item[v, r, s] Values corresponding to the signature of the transaction and used to determine the sender of the transaction; formally $T_w$, $T_r$ and $T_s$. This is expanded in Appendix \ref{app:signing}.
\end{description}

@@

We can assert its validity if and only if it satisfies several conditions: It must be internally consistent with the uncle and transaction block hashes and the given transactions $B_\mathbf{T}$, when executed in order on the base state $\boldsymbol{\sigma}$ (derived from the final state of the parent block), result in a new state of the identity $H_r$:
\begin{equation}
\begin{array}[t]{lclc}
H_u &\equiv& \mathtt{\small SHA3}(\mathtt{\small RLP}(L_H^*(B_\mathbf{U}))) & \wedge \\
H_t &\equiv& \mathtt{\small TRIE}(\{\forall i < \lVert B_\mathbf{T} \rVert, i \in \mathbb{P}: p(i, L_R(B_\mathbf{R}[i])\})) & \wedge \\
H_r &\equiv& \mathtt{\small TRIE}(L_S(\Pi(\boldsymbol{\sigma}, B))) &
\end{array}
\end{equation}

where $p(k, v)$ is simply the pairwise RLP transformation, in this case, the first being the index of the transaction in the block and the second being the transaction receipt:

\begin{equation}
P(k, v) \equiv \big( \mathtt{\small RLP}(k), \mathtt{\small RLP}(v) \big)
\end{equation}

@@

The component types are defined thus:
\begin{equation}
\begin{array}[t]{lclclcl}
H_p \in \mathbb{B}_{32} & \wedge & H_u \in \mathbb{B}_{32} & \wedge & H_b \in \mathbb{B}_{20} & \wedge \\
H_r \in \mathbb{B}_{32} & \wedge & H_t \in \mathbb{B}_{32} & \wedge & H_d \in \mathbb{P} & \wedge \\
H_i \in \mathbb{P} & \wedge & H_m \in \mathbb{P} & \wedge & H_l \in \mathbb{P} & \wedge \\
H_u \in \mathbb{P} & \wedge & H_s \in \mathbb{P} & \wedge & H_x \in \mathbb{B} & \wedge \\
H_n \in \mathbb{B}_{32} &&&&
\end{array}
\end{equation}

@@

The canonical gas limit of a block of header $H$ is defined as $L(H)$:
\begin{eqnarray}
L(H) & \equiv & \begin{cases}
10^6 & \text{if} \quad H_i = 0\\
125000 & \text{if} \quad L'(H) < 125000\\
L'(H) & \text{otherwise}
\end{cases}\\
L'(H) & \equiv & \big\lfloor \frac{1023 {P(H)_H}_l + \lfloor \frac{6}{5}{P(H)_H}_u \rfloor}{1024}\big\rfloor
\end{eqnarray}

$H_s$ is the timestamp of block $H$ and must fulfil the relation:
\begin{equation}
H_s > {P(H)_H}_s
\end{equation}

@@

This is the foundation of the security of the blockchain and is the fundamental reason why a malicious node cannot propagate newly created blocks that would otherwise overwrite (``rewrite'') history. Because the nonce must satisfy this requirement, and because its satisfaction depends on the contents of the block and in turn its composed transactions, creating new, valid, blocks is difficult and, over time, requires approximately the total compute power of the trustworthy portion of the mining peers.

@@

The given \textbf{gasUsed} and \textbf{minGasPrice} must correspond faithfully to the transactions listed. In the case of ${B_H}_m$, the minimum gas price, all transactions included in the transaction receipt must have a gas price, ${T_0}_p$, that is at least this value:
\begin{equation}
\forall \; T \in B_\mathbf{T}: T_p \geq {B_H}_m
\end{equation}

@@

\item[Ethereum Runtime Environment] (aka ERE) The environment which is provided to an Autonomous Object executing in the EVM. Includes the EVM but also the structure of the world state on which the EVM relies for certain I/O instructions including CALL \& CREATE.
